\documentclass[a4paper,12pt]{article}
\usepackage[margin=1.00in]{geometry}

\title{Problem 7\\
\large Testing Report}
\author{Shagun Shagun, ID - 40138455}
 \date{}
\begin{document}
\maketitle %To display the title in the document.
\maketitle
\section{Testing Function2 - tanx}
    \subsection{Brief}
   The test review is based on the test cases developer has mentioned and also the check on the  mapping of each test case with requirements mentioned. The coverage of all test cases are included.
    \subsection{Testing Criteria}
    The developer has mentioned a set of test cases in which all the functions and implementation has been covered. The following are the points based on which this test cases are evaluated
    \begin{enumerate}
        \item Code Execution.
        \item Test Case returning positive responses.
        \item Test Cases mapped to functional requirements.
        \item Coverage of all test cases.
        \item Working of each unit in the program.
        \item Covering input validation.
    \end{enumerate}
    
    \subsection{Results}
    \begin{center}
    \begin{tabular}{||c c c||} 
     \hline
     No. & Description & Result \\ 
     \hline\hline
     1 & Test Cases covers of all possible cases & PASS \\ 
     \hline
     2 & Test Cases covers the exception handling & PASS \\
     \hline
     3 & Requirement mentioned in the problem2 has covered & PASS \\
     \hline
     4 & Working of calculating sin() function & PASS \\
     \hline
     
     \hline
     5 & Working of calculating cos() function & PASS \\
     \hline
     
     \hline
     6 & Working of calculating tan() function & PASS \\
     \hline
     7 & Test on checking input within range & PASS \\
     \hline
     8 & Test cases follows assumptions & Not Applicable \\
     \hline
    \end{tabular}
    \end{center}
    
    \subsection{Result}
    Almost all the methods of function2 have been tested and confirmed to be effective and corrective. During the testing process, no major  mistakes were discovered. All of the requirements given in Problem 2 has been covered in the mentioned test cases. Furthermore, all the test cases are to the point and covered all possibilities.
    
    \subsection{Suggestions}
    Assigning each test case a unique id would make contribution to readability.
    
\end{document}