\documentclass[a4paper,12pt]{article}
\usepackage[margin=1.00in]{geometry}

\title{Problem 5\\
\large Source Code Review}
\author{Shagun Shagun, ID - 40138455}
 \date{}
\begin{document}
\maketitle %To display the title in the document.
\maketitle
\section{Assigned Function - $x^y$}
    \subsection{Standard Guidelines}
   The source code review is based on the standard practices that a developer has used while writing the code. The coverage of all standard guidelines on which the report has generated is listed below.
   \begin{enumerate}
        \item The code should eliminate nested if statement.
       \item The code should follow a coding style guide.
       \item The code should have meaningful method and variable names.
       \item The author should annotate the comments not exceeding 10 to 20 lines.
       \item The class program should not import unnecessary packages.
       \item The code should have low coupling and high cohesion.
       \item The code should avoid the global scoping for common variables and functions.
       \item The code should avoid memory leakage.
       \item The code should narrow the variable scope as far as possible in the code.
       \item Usage of mutable variable over creating new variables in object oriented language.
   \end{enumerate}
   
    \subsection{Review Approach}
    Used Approach - Lightweight Code Review
    \begin{itemize}
        \item Walk-through the code.
        \item Executed the code in run time environment and also used debugger.
        \item Inspection on comment length, Checking dependencies among the components, Check on unused variables.
        \item Observing global scoping of the functions and variables.
    \end{itemize}
    
    \subsection{Results}
    \begin{center}
    \begin{tabular}{||c c c||} 
     \hline
     No. & Description & Result \\ 
     \hline\hline
     1 & Use of annotation in the code  & PASS \\ 
     \hline
     2 & No usage of nested ifs statement & PASS \\
     \hline
     3 & No unused variable found & PASS \\
     \hline
     4 & No memory leakage & PASS \\
     \hline
     
     \hline
     5 & Usage of meaningful method and variable names & PASS \\
     \hline
     
     \hline
     6 & Not exceeding source line of  code & PASS \\
     \hline
     7 & No deadlock encountered & PASS \\
     \hline
     8 & No dependency found in the code & PASS \\
     \hline
     9 & No Error found in the code & PASS \\
     \hline
     9 & No Warning found in the code & PASS \\
     \hline
     10 & No unnecessary package is included in the code  & PASS \\
     \hline
    \end{tabular}
    \end{center}
    
    \subsection{Conclusion}
    Overall, the code is well-structured and well-written. It is clear from the code that readability is a developer's primary focus. The only suggestion I have is to retain logs because they can help with debugging.
\end{document}