\documentclass[a4paper,12pt]{article}
\usepackage[margin=1.00in]{geometry}
\title{Problem 6\\
\large Standard Guidelines Used for Function 5}
\author{Shagun Sharma, ID - 40138455}
 \date{}
\begin{document}
\maketitle
\section{Standard Guidelines}
    The following are the guidelines implemented in the unit testing for function 5 :
    \begin{equation} \label{Power_func}
	f(x) = ab^x
\end{equation}

\begin{itemize}
    \item Each test case should given a test case id.
    \item Each test should contains the unit test of each function involved in the implementation of function 5.
    \item Each test case is followed by one line statement justifying it's description.
    \item Each test case contains the function name used in the unit test case.
    \item Test case shall cover all the cases expected.
    \item Test Case should mention a expected value and actual value.
    \item Atleast one test case should be consider into a delta precision values.
    \item Each test case should show message or log for the sake of readability.
    \item Each test case should be traceable.
    \item Test case should map to the functional requirement.
\end{itemize}

\section{Implemented Unit Test}
\begin{itemize}
    \item  Unit Testing Framework Used: JUnit
    \item The sample practice used in the test cases are as follows:\\
    \\ID = TC1
 \\Test  Case =  description about the test case.
 \\Function Used = name of the function used in the test case.
 \\Functional Requirement ID Used = FRn
\end{itemize}
   
 
 \


\end{document}
