\documentclass[a4paper,12pt]{article}

% defining margin for the document
\usepackage[margin=1.00in]{geometry}

% these packages are used for images
\usepackage{graphicx}

\title{Problem 5: Source Code Review}
\author{Saraswati Saud \\
Student ID: 40115097}
\date{}
\begin{document}
\maketitle
\section{Source code review of Function F5: ab$^x$}
    \subsection{Introduction}
    The function provided for the source code review purpose was ab$^x$ is a power function. The code was reviewed based on the coding standards that the developer has followed while writing the code. For this, I reviewed coding practices, non-functional requirements and overall structure of the code.
    
    \subsection{Code Review Checklist}
    Following are the checklists of the standard code review guidelines which was used for reviewing the source code:
    \begin{enumerate}
        \item Don’t repeat yourself (Avoid duplication)
        \item Functionality of the code should work properly
        \item Use of meaningful class, method and variables names
        \item Don’t ignore the exception in the code
        \item Avoid creating unnecessary class, methods, variables and objects.
        \item Proper comments have been added
        \item Unnecessary packages should not be imported
        \item Class, function should not be too lengthy
        \item Code must have unit test cases
        \item Proper error message should be displayed
    \end{enumerate}
    
    \subsection{Review Approach}
    Several steps were followed while reviewing the source code.
    \begin{itemize}
        \item First, the code was reviewed well enough to check the naming convention, proper comments in the class and methods, and test cases.
        \item Second, the code was run to check whether the functionality properly works or not.
        \item Third, test cases were run to check whether all the test cases pass or not.
    \end{itemize}
    
    \subsection{Code Review Results}
    \begin{center}
    \begin{tabular}{||c c c||} 
     \hline
     Checklist & Description & Result \\ 
     \hline\hline
     1 & Duplicate Code & PASS \\ 
     \hline
     2 & Functionality of the code & PASS \\
     \hline
     3 & Naming Convention & PASS \\
     \hline
     4 & Exception Handling & PASS \\
     \hline
     5 & No unnecessary class, methods and variables & PASS \\ 
     \hline
     6 & Useful comments & PASS \\
     \hline
     7 & No unnecessary imports & PASS \\
     \hline
     8 & No lengthy code & PASS \\
     \hline
     9 & Must have unit test cases & PASS \\
     \hline
     10 & Proper error message & PASS \\
     \hline
    \end{tabular}
    \end{center}
    
    \subsection{Conclusion}
    From the above, it is noted that the code is well written and all the necessary quality attributes are fulfilled. The only flaw I could found was missing few comments in the function body.
\end{document}
