\documentclass[a4paper,12pt]{article}

% defining margin for the document
\usepackage[margin=1.00in]{geometry}

% these packages are used for images
\usepackage{graphicx}

\title{Problem 4: Quality Attributes}
\author{Saraswati Saud \\
Student ID: 40115097}
\date{}
\begin{document}
\maketitle
\section{Quality Attributes}
    Following are the efforts that has been made in achieving the quality attributes:
    \subsection{Correctness}
    \begin{itemize}
        \item ‘Standard’ programming style for the source code has been followed.
        \item Related test cases have been added on the assigned functions.
    \end{itemize}
    
    \subsection{Efficient}
    \begin{itemize}
        \item Program takes less time to execute.
        \item Unnecessary variables, methods and the statements have been removed.
    \end{itemize}
    
    \subsection{Maintainability}
    \begin{itemize}
        \item Programming style has been made identical throughout the team to remove ambiguity.
        \item Necessary comments have been added where required.
    \end{itemize}
    
    \subsection{Robustness}
    \begin{itemize}
        \item Proper error handling has been done for the wrong user inputs.
        \item Use of Try…Catch block for handling java exceptions.
    \end{itemize}
    
    \subsection{Usable}
    \begin{itemize}
        \item Simple textual interface has been added for user input and output.
        \item Proper error messages have been given for the wrong inputs.
        \item Proper display of an output has been done for the right inputs.
    \end{itemize}
    
\end{document}
